### 2024-11-09 conteudo/tool/tool.tex
add ref to github implementation of the tool
Reviewing tool proposal - part 1

Our proposed tool is a Command Line Interface (CLI) software. Its purpose is to enable developers to query 
information about code clone duplication at the function level, which means finding pairs of functions in a codebase 
that are code clones of each other.

The tool operates in two steps. The first step, called Setup, is executed only 
once for each codebase and is responsible for processing the codebase by extracting functions from code files and 
searching for code clone duplications. The second step, called Query Responder, executes the tool's functionalities 
using the information obtained in the Setup step. More information about the Setup and Query Responder behavior can 
be found in sections \ref{subsec:architecture}  and \ref{subsec:func}.

>>>>

Our proposed tool is a Command Line Interface (CLI) application designed to
help developers identify code clone duplication at the function level.
Specifically, it enables the detection of pairs of functions within a codebase
that are clones of each other.

The tool operates in two main steps. The first step, called *Setup*, is
executed only once for each codebase. This step processes the codebase by
extracting functions from code files and identifying code clone duplications.
The second step, called *Query Responder*, utilizes the information obtained in
the Setup phase to execute the tool’s functionalities as needed. Detailed
descriptions of the Setup and Query Responder processes can be found in
Sections \ref{subsec:architecture} and \ref{subsec:func}.

The tool has been implemented and is available for reference at
\url{https://github.com/LipArcanjo/test-duplication-code}.
